---
title: "P8105 Homework 4"
author: "Laylah Jones"
date: 2023-11-15
output: github_document
---

```{r, include=FALSE}
library(tidyverse)
library(rvest)
library(readr)
library(broom)
library(dplyr)

options(readr.show_col_types = FALSE)

knitr::opts_chunk$set(
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = ("viridis"))

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1



# Problem 2

## Load the data

```{r, col_types = FALSE}
study_df = 
  tibble(
    files = list.files("data/"),
    path = str_c("data/", files)) |> 
  mutate(data = map(path, read_csv)) |> 
  unnest(c(data))

study_df
```

## Tidy the data
```{r}
tidy_study_df = 
  study_df |> 
  separate(files, into = c("control_arm", "subject_ID", "csv")) |> 
  mutate(
    control_arm = ifelse(control_arm == "con", "control", control_arm),
    control_arm = ifelse(control_arm == "exp", "experimental", control_arm)
  ) |> 
  pivot_longer(
    cols = starts_with("week"), 
    names_to = "week", 
    names_prefix = "week_",
    values_to = "observation") |> 
  select(subject_ID, control_arm, week, observation) |> 
  mutate(week = as.numeric(week))

tidy_study_df
```


## Spaghetti Plot of Observations on Each Subject Over Time

```{r}
study_plot = 
  tidy_study_df |> 
  ggplot(aes(x = week, y = observation, color = subject_ID)) +
  geom_point() +
  geom_line() +
  facet_grid(.~control_arm) + 
  labs(
    x = "Week",
    y = "Observation",
    title = "Observations for Each Subject by Week"
  )

study_plot
```

From this plot, we can observe that the control arm had lower values than the experimental arm. The control arm has observations that are consistently between the range of approximately -2.17 and 4.26 for each subject in all eight weeks, with the lowest observation value of -2.17 in week six for subject 5 and the highest observation value of 4.26 in week five for subject 10. The experimental arm has observations that are consistently between the range of approximately -0.84 and 7.66 for each subject in all eight weeks, with the lowest observation value being in week one for subject 2 and the highest observation value being in week seven for subject 6.


# Problem 3

## Setting the Design Elements and Generating 5000 Datasets

```{r, message = FALSE}
n = 30
sigma = 5
mu = 0
alpha = 0.05
set.seed(12345)

sim_norm = function(mu, n = 30, sigma = 5) {
  
  sim_data = tibble(
    x = rnorm(mean = mu, n = n, sd = sigma),
  )
  
  sim_data |>  
    t.test(mean = 0, alternative = "two.sided", conf.level = 0.95) |> 
    broom::tidy() |> 
    select(p.value, estimate) |> 
    rename(mu_hat = estimate)
}
```

```{r}
sim_results_df = 
  expand_grid(
    mu = c(0,1,2,3,4,5,6),
    iter = 1:500
  ) |> 
  mutate(
    estimate_df = map(mu, sim_norm)
  ) |> 
  unnest(estimate_df)
```

## Plot Showing the Proportion of Times the Null was Rejected

```{r}
sim_results_plot = 
  sim_results_df |> 
  group_by(mu) |> 
  mutate(
    reject = case_when(
      p.value > 0.05 ~ FALSE,
      p.value < 0.05 ~ TRUE
    )) |> 
  summarize(count = sum(reject)) |> 
  mutate(prop = count / 500)

sim_results_plot |> 
  ggplot(aes(x = mu, y = prop, fill = mu)) +
  geom_point() +
  geom_line() +
  labs(
    title = "Proportion of Times the Null Hypothesis was Rejected for Each Mu",
    x = "True Value of Mu",
    y = "Proportion of Times Rejected"
  )
```

## Plot Comparing the Average Estimate and the True Value of Mu

```{r}

```



