---
title: "P8105 Homework 4"
author: "Laylah Jones"
date: 2023-11-15
output: github_document
---

```{r, include=FALSE}
library(tidyverse)
library(rvest)
library(readr)

options(readr.show_col_types = FALSE)

knitr::opts_chunk$set(
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = ("viridis"))

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1



# Problem 2

## Load the data

```{r, col_types = FALSE}
study_df = 
  tibble(
    files = list.files("data/"),
    path = str_c("data/", files)) |> 
  mutate(data = map(path, read_csv)) |> 
  unnest(c(data))

study_df
```

## Tidy the data
```{r}
tidy_study_df = 
  study_df |> 
  separate(files, into = c("control_arm", "subject_ID", "csv")) |> 
  mutate(
    control_arm = ifelse(control_arm == "con", "control", control_arm),
    control_arm = ifelse(control_arm == "exp", "experimental", control_arm)
  ) |> 
  pivot_longer(
    cols = starts_with("week"), 
    names_to = "week", 
    names_prefix = "week_",
    values_to = "observation") |> 
  select(subject_ID, control_arm, week, observation) |> 
  mutate(week = as.numeric(week))

tidy_study_df
```


## Spaghetti Plot of Observations on Each Subject Over Time

```{r}
study_plot = 
  tidy_study_df |> 
  ggplot(aes(x = week, y = observation, color = subject_ID)) +
  geom_point() +
  geom_line() +
  facet_grid(.~control_arm) + 
  labs(
    x = "Week",
    y = "Observation",
    title = "Observations for Each Subject by Week"
  )

study_plot
```

The control arm has observations that are consistently between the range of approximately -2.17 and 4.26 for each subject in all eight weeks, with the lowest observation value of -2.17 in week six for subject 5 and the highest observation value of 4.26 in week five for subject 10. The experimental arm has observations that are consistently between the range of approximately -0.84 and 7.66 for each subject in all eight weeks, with the lowest observation value being in week one for subject 2 and the highest observation value being in week seven for subject 6.


# Problem 3

## Setting the Design Elements
```{r}
set.seed(12345)

sim_function = function(n = 30, sigma = 5, mu = 0) {
  
  sim_df = tibble(
    x = rnorm(n = 30, mean = mu, sd = sigma),
  )
  
  sim.df |> 
    t.test(conf.level = 0.95) |> 
    broom::tidy() |> 
    select(estimate, p.value)

}

```

